\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING---------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE ANAY SINHAL}} & Gainesville, FL, USA \\
  Email: \href{mailto:sinhal.anay@ufl.edu}{sinhal.anay@ufl.edu} & Mobile: +1 (352) 219-5579 \\
  GitHub: \href{https://github.com/anayy09}{anayy09} & LinkedIn: \href{https://www.linkedin.com/in/anaysinhal/}{in/anaysinhal} \\
  Portfolio: \href{https://www.anay.codes/}{anay.codes} & Available for Summer 2026 internships (May to Aug 2026) \\
\end{tabular*}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL, USA}
      {M.S. Computer \& Information Science \& Engineering}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Graduate and CISE Senior Certificate coursework (Spring 2025) GPA: 3.91/4.00}
        \resumeItem{Expected graduation Dec 2026.}
      \resumeItemListEnd
    \resumeSubheading
      {JK Lakshmipat University}{Jaipur, India}
      {B.Tech. Computer Science \& Engineering}{Aug 2021 -- May 2025}
      \resumeItemListStart
        \resumeItem{CGPA: 8.76/10.}
        \resumeItem{Semester Exchange, \textbf{Indian Institute of Technology Kanpur}, Spring 2024.}
        \resumeItem{Semester Exchange, \textbf{Indian Institute of Technology Gandhinagar}, Fall 2022.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, Java, JavaScript/TypeScript, Go, C++, Gleam} \\
      \textbf{AI/ML}{: PyTorch, TensorFlow, scikit-learn, Hugging Face, NLP, Computer Vision, LLM fine-tuning} \\
      \textbf{Web}{: React, Next.js, Node.js, Django, FastAPI, Spring Boot, HTML/CSS} \\
      \textbf{Data \& Infra}{: PostgreSQL, MongoDB, Redis, SQL, Docker, Git, CI/CD, AWS, Bash} \\
      \textbf{Tools}{: Postman, Figma}
    }}
 \end{itemize}

%----------- EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Intelligent Clinical Care Center (IC3), University of Florida}{Gainesville, FL, USA}
      {Graduate Student Assistant}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Build Dockerized ETL pipelines to ingest and harmonize multi site clinical and environmental datasets into research ready schemas.}
        \resumeItem{Standardize workflows and logging across HiPerGator and on prem deployments, cutting environment setup and onboarding time for new analyses.}
      \resumeItemListEnd

    \resumeSubheading
      {Indraprastha Institute of Information Technology Delhi (IIIT-D)}{New Delhi, India}
      {Research Assistant}{Sep 2024 -- Oct 2024}
      \resumeItemListStart
        \resumeItem{Developed full stack applications (Next.js, Node.js, PostgreSQL) backing AI based cancer and ECG diagnostic models.}
        \resumeItem{Set up CI/CD pipelines with automated testing to reduce manual release overhead and keep production models in sync with research updates.}
      \resumeItemListEnd

    \resumeSubheading
      {GeeksforGeeks}{Noida, India}
      {Software Development Intern}{May 2024 -- Sep 2024}
      \resumeItemListStart
        \resumeItem{Rebuilt core content pages (Articles, Videos, Quizzes) using Next.js and React to improve load times and responsiveness over legacy PHP views.}
        \resumeItem{Implemented structured data and server side rendering that improved search visibility for high traffic pages.}
      \resumeItemListEnd

    \resumeSubheading
      {Sardar Vallabhbhai National Institute of Technology Surat (SVNIT)}{Remote}
      {Research Intern}{May 2024 -- Jul 2024}
      \resumeItemListStart
        \resumeItem{Built a contrastive learning pipeline with BERT for depression detection on DepressionEmo, reaching F1 score of 0.81.}
        \resumeItem{Improved F1 score by about 10 \% over baseline BERT through better contextual representation and training strategy.}
      \resumeItemListEnd

    \resumeSubheading
      {Indian Institute of Technology Jammu (IIT Jammu)}{Remote}
      {Research Intern}{Dec 2023 -- Jan 2024}
      \resumeItemListStart
        \resumeItem{Developed a stacking ensemble (Random Forest, XGBoost, MLP) for stress detection on 11.5M wearable sensor records with 93.7 \% macro F1 and 14.5 ms inference latency.}
        \resumeItem{Used SMOTE Tomek resampling to lift recall for the minority chronic stress class by 37 \% over standard oversampling.}
      \resumeItemListEnd

    \resumeSubheading
      {Dexpert Systems Pvt. Ltd.}{Pune, India}
      {Software Development Intern}{Jun 2023 -- Jul 2023}
      \resumeItemListStart
        \resumeItem{Integrated React front end with Spring Boot and Laravel services for Zoho CRM workflows, cutting lead assignment latency from minutes to near real time.}
        \resumeItem{Designed REST APIs with JWT based authentication and delivered Docker Compose stacks and documentation for handoff.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{\href{https://github.com/anayy09/ehr-timeline-triage}{EHR Timeline Triage}} $|$ \emph{Python, PyTorch, FastAPI, Next.js, DuckDB, Docker}}{\textit{Nov 2025}}
    \resumeItemListStart
      \resumeItem{Built a research prototype that converts longitudinal EHR events into fixed-width time bins \& trains LR, GRU, \& Transformer models for 30 day readmission \& 48 hour ICU mortality prediction with AUROC, AUPRC, Brier score, \& calibration evaluation.}
      \resumeItem{Exposed the models through a FastAPI service \& interactive timeline UI that surfaces risk trajectories \& feature attribution based explanations over synthetic EHR cohorts.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/anayy09/radiology-copilot}{Radiology Copilot}} $|$ \emph{PyTorch, MONAI, FastAPI, Next.js, Express, PostgreSQL, Docker}}{\textit{Nov 2025}}
    \resumeItemListStart
      \resumeItem{Developed a full stack radiology decision support app where clinicians can upload chest X ray studies, run a multimodal CLIP style model that combines ViT image encoder \& ClinicalBERT text encoder, \& obtain multi label findings with calibrated uncertainty.}
      \resumeItem{Integrated Grad CAM saliency overlays, AI drafted radiology reports, \& a study store backed by PostgreSQL behind a Next.js dashboard with study lifecycle tracking \& editing or export workflow.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/anayy09/Medlyze}{Medlyze: AI Powered Diagnostic Support Platform}} $|$ \emph{Next.js 15, PostgreSQL/Prisma, Tailwind, LLM}}{\textit{Oct 2025}}
    \resumeItemListStart
      \resumeItem{Implemented encrypted medical report intake with AES 256 file encryption, regex based de identification, \& role based access for patients \& clinicians.}
      \resumeItem{Added multimodal analysis across PDFs \& images using LLM \& vision models with longitudinal biomarker tracking \& risk scoring views.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{\href{https://github.com/anayy09/Sepsis-Sentinel}{Sepsis Sentinel}} $|$ \emph{Python, FastAPI, XGBoost, React, Docker, PostgreSQL}}{\textit{Jul 2025}}
    \resumeItemListStart
      \resumeItem{Trained XGBoost \& LightGBM models for early sepsis detection from EHR data with AUROC 0.89 on validation cohorts.}
      \resumeItem{Built a FastAPI service \& React dashboard to surface risk scores \& trends, showing up to 4 hour earlier alerts in simulation.}
    \resumeItemListEnd

    % \resumeProjectHeading
    %   {\textbf{\href{https://github.com/anayy09/Finmate}{FinMate: Personal Finance Manager}} $|$ \emph{Django, React, Chakra UI, D3, Plotly}}{\textit{Jun 2025}}
    % \resumeItemListStart
    %   \resumeItem{Integrated Plaid API, Random Forest forecasts, \& Isolation Forest anomaly detection in a Django backend to generate monthly PDF \& CSV spend reports.}
    %   \resumeItem{Developed a React dashboard with interactive charts \& budget alerts via email \& in app notifications.}
    % \resumeItemListEnd

    % \resumeProjectHeading
    %   {\textbf{\href{https://github.com/anayy09/Local-News-Analytics}{Intelligent Local News Analytics Platform}} $|$ \emph{Python, spaCy, BERTopic, BART, Flask}}{\textit{Apr 2025}}
    % \resumeItemListStart
    %   \resumeItem{Built an NLP pipeline that clusters over 2k news items per day \& flags emerging events with F1 score 0.83.}
    %   \resumeItem{Deployed a Flask dashboard with scheduled updates to reduce manual monitoring effort for editors.}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small

  \item \textbf{Contrastive Learning and Large Language Models for Depression Detection from Social Media.}\\
  \textit{IEEE International Conference on Contemporary Computing \& Communications}, Dec 2025.
  \href{https://doi.org/10.1109/InC465408.2025.11256322}{DOI: 10.1109/InC465408.2025.11256322}
  
  \item \textbf{Battery-Aware Super-Peer and Fountain Coding in Java P2P Systems.}\\
  \textit{Discover Internet of Things}, Springer Nature, Nov 2025. \href{https://doi.org/10.1007/s43926-025-00240-3}{DOI: 10.1007/s43926-025-00240-3}.

  \item \textbf{Optimizing Diagnostic Accuracy in Healthcare by Using Deep Learning.}\\
  \textit{IEEE 4th World Conference on Applied Intelligence \& Computing (AIC)}, Nov 2025. \href{https://doi.org/10.1109/AIC66080.2025.11211920}{DOI: 10.1109/AIC66080.2025.11211920}.

  \item \textbf{LoRA-Tuned Segment Anything Model for Few-Shot Polyp Segmentation in Colonoscopy Images.}\\
  \textit{Journal of Carcinogenesis}, Sept 2025. \href{https://doi.org/10.64149/J.Carcinog.24.3.372-386}{DOI: 10.64149/J.Carcinog.24.3.372-386}.

  \item \textbf{Stress Monitoring in Healthcare: An Ensemble Machine Learning Framework Using Wearable Sensor Data.}\\
  \textit{International Conference on Innovations in Computational Intelligence \& Computer Vision}, accepted; to appear in Springer.


\end{itemize}


%-----------PATENTS-----------
\section{Patents}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{
    \item \textbf{A Method for Disaster-Resilient Digital File Dissemination via Fountain-Coded Broadcast with Super-Peer Election and Sparse Acknowledgement.} \\
    Indian Patent Application No. 202511063465, published Jul 2025.

    \item \textbf{A Stress Monitoring System Using Wearable Sensor Data Integrated with an Ensemble Machine-Learning Model.} \\
    Indian Patent Application No. 202511044124, published May 2025.
  }
\end{itemize}



%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Graduate:} Distributed Operating Systems Principles, Analysis of Algorithms, Advanced Data Structures, Computer Networks, Software Engineering, Data Science. \\
    \textbf{Undergraduate:} Database Systems, Machine Learning, Object Oriented Programming.
  }}
\end{itemize}

\end{document}
